\lettrine[lines=2,lraise=0]{W}hoosh! Mechano speeds away in his bad guy plane. 

He yells, ``You'll never catch me rescue rangers! I'm the best pilot ever! Go back to your sad little headquarters so I can blow you all up!''

The rescue rangers yell back, ``Never! We will never allow you to destroy our headquarters!''

Just then one of the rescue rangers hits Mechano's plane from the top and he starts spiralling down. He yells out, ``Aaarrrggghhh'' and the rescue ranger yells back, ``You're the best pilot ever, how silly.''

Mechano pulls back hard on his yoke and it goes, ``creak!'' and his plane pulls up into the air again straight at the ranger.

Mechano yells at the ranger, ``How dare you treat me with such insolence! I am superior! You are destined to be my slaves, that is if you are not destroyed first. Surrender, and perhaps I may spare you. Perhaps I will choose you to be my slaves---''

Mechano's guns blaze and shred the rangers plane, ``budda budda budda---'' and the ranger spirals down in smoke and flame. He ejects and his plane his a cliff kaboom! When he lands he stumbles away to put bandaids on his bobos.

There are 8 more ranger planes, he hits another, ``budda budda budda'' and it goes down. a ranger plane right beside it banks hard to the side when mechano fires again, ``budda budda budda'' and he misses but when the ranger banked away there is another ranger farther away. Mechano picks the target, ``beep... beep... beep. beep. beepbeepbeep'' and he releases his superpower sidewinder missile, ``whoosh!'' as mechano pulls his plane up and backwards. The ranger plane banks hard to the left and releases a burning torch because he knows the super sidewinder missile finds hot things yummy and might decide to blow up the torch instead. Having conpleted his upsy downy move Mechano comes down on the closer plane from above, ``budda budda budda'' and the ranger blows up! 

Oh no! The remaining rangers talk on their super secret radios.

``Whatever will we do?'' said one ranger.

``He really is the best pilot ever!'' said another.

``Retreat everybody! We have to go back to headquarters! He may be the best pilot ever but we have the best gunner ever!''

``Of course! you're right! That's how we can save the day!''

So the remaining planes go back to headquarters. They turn on their overcharger afterburners to go super fast and get away from Mechano. You see they learned Mechanos planes can move around really easily but isn't very fast. They heard him cackling as they left, because they are going into the trap he hoped they would.